Title Goes Here

### 2023-09-26 paper/main.tex
some protocol descriptions

@@

@@

\subsection{Secure Protocols Evaluated}

\begin{table}
\centering
  \begin{tabular}{|l | l|l|}
    \hline
    \textbf{Protocol} & \textbf{Purpose} & \textbf{Ref.} \\
    \hline
    $n$-bit Addition & Custom & TODO \\
    Oblivious Transfer & Building block & TODO \\
    OT Extension & Building block & TODO \\
    Beaver Triple Generation & Building block & TODO \\
    GMW & Circuit evaluation & TODO \\
    MPC w/ Beaver Triples & Circuit evaluation & TODO \\
    \hline
  \end{tabular}
  \caption{Secure protocols used in our evaluation.}
\end{table}

\begin{table}
\centering
  \begin{tabular}{|l |l|l|}
    \hline
    \textbf{Circuit} & \textbf{AND Gates} & \textbf{Total Gates} \\
    \hline
    64-bit adder & 63 & 376 \\
    64-bit multiplier & 4,033 & 13,675 \\
    AES-128 & 6,400 & 36,663 \\
    SHA-256 & 22,573 & 135,073 \\
    Floating-point division & 82,269 & 184,007 \\
    \hline
  \end{tabular}
  \caption{Circuits used in our evaluation.}
\end{table}

>>>>

\renewcommand{\paragraph}[1]{\vspace*{2pt}\noindent\textbf{#1}}

\newcommand{\system}{\textsc{SystemName}\xspace}

@@

\section{Case Study Protocols}

For our evaluation, we implemented six MPC protocols from the literature in \system, and evaluated \system's scalability and ability to find implementation bugs in these protocols. The six protocols are listed in Table~\ref{tbl:protocols}. One is a simple addition protocol, three are basic building blocks often used to build more complex protocols, and two are protocols designed to securely evaluate circuits. All six protocols are designed for two parties, with the addition of a third ``dealer'' party to produce correlated randomness in several of the protocols.

\begin{table}
\centering
  \begin{tabular}{|l | l|l|}
    \hline
    \textbf{Protocol} & \textbf{Purpose} & \textbf{Ref.} \\
    \hline
    $n$-bit Addition & Custom & TODO \\
    Oblivious Transfer & Building block & TODO \\
    OT Extension & Building block & TODO \\
    Beaver Triple Generation & Building block & TODO \\
    GMW & Circuit evaluation & TODO \\
    MPC w/ Beaver Triples & Circuit evaluation & TODO \\
    \hline
  \end{tabular}
  \caption{Secure protocols used in our evaluation.}
  \label{tbl:protocols}
\end{table}

\paragraph{$n$-bit Addition.}
The simplest protocol in our evaluation is a basic summation protocol, which adds up the inputs from the two participating parties. To accomplish this task, the protocol essentially simulates a hardware adder circuit---for each bit in the binary representation of the two input numbers, the protocol performs bitwise operations to compute the sum and carry bit. To ensure security, the input values are \emph{secret shared} using additive secret sharing; to secret share a bit, a party selects a random bit to represent one share, and computes the other share by XORing the random bit with the secret bit. In \system, $P_1$ can secret share the bit $x$ with $P_2$ as follows:
%
\begin{verbatim}
  s1 = FLIP @P1
  s2 = x + s1
  SEND s1 TO P2
\end{verbatim}
%
$P_1$ can safely send one share to $P_2$, as long as $P_1$ keeps the other share for themselves---neither share alone reveals anything about the secret bit. To add (i.e. XOR) two secret-shared bits, each party can simply add its shares for the two bits to obtain one share of the result. To multiply (i.e. AND) two secret-shared bits, the parties must use oblivious transfer (described next).

Our $n$-bit addition protocol generates a \system source file for a given bitwidth. In our evaluation, we test several different bitwidths to examine the effect of the size of each party's view on the scalability and bug-finding capability of \system.

\paragraph{Oblivious Transfer.}
Oblivious transfer~\cite{todo} (OT) is a 2-party protocol that allows one party ($R$, the \emph{receiver}) to select one out of several secret inputs provided by the other party ($S$, the \emph{sender}). In 1-out-of-2 OT, $S$ provides 2 secret inputs $x_0$ and $x_1$ and $R$ provides a secret \emph{selection bit} $b$. If $b=0$, $R$ receives $x_0$; if $b=1$, $R$ receives $x_1$. $R$ does not learn anything about the not-selected secret, and $S$ does not learn which secret $R$ selected. This idea can be extended to 1-out-of-$n$ OT by extending the selection bit $b$ to a $\log_2(n)$-bit string.
%
Oblivious transfer is a building block for many other protocols. For example, the GMW protocol for circuit evaluation (described later) evaluates AND gates using 1-out-of-4 OT

\paragraph{Oblivious Transfer Extension.}
Protocols like GMW (described later) require the use of OT for each AND gate---for large circuits, this means thousands or millions of OTs. \emph{OT extension}~\cite{todo} is an approach for expanding $k$ ``base'' OTs into $m \gg k$ OTs. OT extension can significantly improve the performance of protocols that use many OTs.

\paragraph{Beaver Triple Generation.}
A \emph{Beaver triple}~\cite{todo} (or \emph{multiplication triple}) is a set of secret shares of numbers $a$, $b$, and $c$ such that $a \cdot b = c$. To use a Beaver triple, $P_1$ must have one share of each of $a$, $b$, and $c$, and $P_2$ must have the other share. Since the values are secret shared, they appear random to each party---but the correlation between the three numbers can be used to perform efficient multiplication between secret-shared numbers (described later). One Beaver triple must be consumed for each multiplication, but they can be generated in a separate offline phase. Beaver triples can be generated by a trusted ``dealer'' party, or by using oblivious transfer. We implement both versions in \system.

\paragraph{GMW (Goldreich-Micali-Widgerson.}

\paragraph{MPC with Beaver Triples.}

\paragraph{Circuits.}
To evaluate the circuit-based protocols, we used five binary circuits that are publicly available in the ``Bristol-fashion'' format~\cite{todo}. We chose commonly-used circuits with a range of sizes to test \system's scalability. Table~\ref{tbl:circuits} lists the circuits used in our evaluation, along with the number of gates in each circuit.

\begin{table}
\centering
  \begin{tabular}{|l |l|l|}
    \hline
    \textbf{Circuit} & \textbf{AND Gates} & \textbf{Total Gates} \\
    \hline
    64-bit adder & 63 & 376 \\
    64-bit multiplier & 4,033 & 13,675 \\
    AES-128 & 6,400 & 36,663 \\
    SHA-256 & 22,573 & 135,073 \\
    Floating-point division & 82,269 & 184,007 \\
    \hline
  \end{tabular}
  \caption{Circuits used in our evaluation.}
  \label{tbl:circuits}
\end{table}

@@
